---
title: "Insurance purchase prediction"
output: html_document
---

**This project is done in submission to the CS107 class final project requirement**

In this project I will try to predict the purchase of a specific insurance package (package G) based on the transaction history of other purchases and also the user related data.

The reson for choosing the G insurance package is, referring to the competition forums, G is the main variable that changes from year to year
Coming up with a model to predict the G value correctly led to very good results on the test data set

## Loading Data

Data for this project is taken from the kaggle website where the competition is hosted. Due to the limitations of data set size and current PC limitations, I will be using only the test data set

I downloaded the data from website and stored it in my local repository

```{r}
library(readr)
library(dplyr)
test <- read.csv ('test_v2.csv', header=T, stringsAsFactors = F)
```

### Data clean up

In this step we will be eliminating all the rows with incomplete data

```{r}
test <- na.omit(test)
```

Also we will be removing the columns that are not used for the prediction. 
We will be excluding the day, time and cost columns in this analysis

```{r}
test <- test[, !(colnames(test) %in% c("day","time","cost"))]
```

### Checking the colum type of G
```{r}
is.factor(test$G)
```
 
upon checking we notice that this is not currently stored as factor variable. 
We will converting this column variable to a factor.
```{r}
test$G = as.factor(test$G)
```

### Building Model

In first step, we will try building a multinomial logistic regression model. 
For this we will be using the multinom function from nnet package

```{r}
test$G2 <- relevel(test$G, ref = "1")

library(nnet)
```

Also we will be first trying to predict G based on the purchases of other insurance packages (A to F)

```{r}
model1 <- multinom(G2 ~ A+B+C+D+E+F, data = test)

summary(model1)
```

Now that we have built our first model, we will try identifying the significant variables for this model. 
For this will be building the z score and p values

```{r}
z <- summary(model1)$coefficients/summary(model1)$standard.errors
z
```

```{r}
p <- (1 - pnorm(abs(z), 0, 1))*2
p
```
Notice that almost all the variables are significant in predicting G


### Multinomial regression with all variables

We will now try to implement a similar model including all the variables

```{r}
model2 <- multinom(G2 ~ ., data = test)

summary(model2)
```

Using the new model to build a prediction data set

```{r}
predicted = predict(model2,test,type="probs")
head(predicted)
```

```{r}
bpp=cbind(test, predicted)
head(bpp)
```

### Trying Ordinal Logistic Regresssion (OLR) approach

```{r}
library(foreign)
library(ggplot2)
library(MASS)
library(Hmisc)
```

```{r}
olr_model1 <- polr(G2 ~ A+B+C+D+E+F, data = test, Hess=TRUE)
summary(olr_model1)
```

we will try identifying the significant variables for this model. 
For this will be building the z score and p values

```{r}
ctable <- coef(summary(olr_model1))
ctable
```

```{r}
ctable <- coef(summary(olr_model1))
ctable
```

```{r}
p <- pnorm(abs(ctable[, "t value"]), lower.tail = FALSE) * 2

ctable <- cbind(ctable, "p value" = p)
ctable
```


### Trying OLR approach with all the variables included

```{r}
# olr_model2 <- polr(G2 ~ ., data = test, Hess=TRUE)
```

When we try the OLR model with variables we notice that the fit doesn't converge



### Refernces
https://www.kaggle.com/c/allstate-purchase-prediction-challenge
http://www.ats.ucla.edu/stat/r/dae/mlogit.htm
http://www.r-bloggers.com/how-to-multinomial-regression-models-in-r/
http://www.analyticsvidhya.com/blog/2016/02/multinomial-ordinal-logistic-regression/
https://github.com/justmarkham/kaggle-allstate
https://github.com/B1aine/kaggle-allstate


















